Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
commit

library(dplyr)
install.packages("ggpubr")
library("ggpubr")

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(authoryearId, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = authoryearId, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

@@

p2 <- p2 + 
  ggplot2::ggtitle("Outbreak investigation")

p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)

@@

## Risk of bias in studies included in review question 1 and review question 2.
*In progress.*
```{r screenplot, echo=FALSE}
p1
```

>>>>

library(dplyr)
#install.packages("ggpubr")
library("ggpubr")

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

@@

p2 <- p2 + 
  ggplot2::ggtitle("Outbreak investigation")
p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)

png("q1_1_new.png", height = 1500, width = 1100)
p3
dev.set(dev.next())
dev.off()

@@

## Risk of bias in studies included in review question 1 and review question 2.

![ROB Q1_1](q1_1_new.png)
